Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
abstract

\begin{abstract}
% We do not say this project, is more like: In this paoer an evolutionary ... 
% is presented or In this paper we present a .... (in third or first person plural) - MG   
In this paper an evolutionary computation-based system is proposed to generate 
levels for the angry birds video game, the levels themselves are composed of a 
set of birds that the player can use, a set amount of pigs that must be destroyed 
in order to progress to the next level and a given number of pieces that conform 
structures that may or may not protect the pigs from the player, this level 
generation system can create composites of pieces in order to create structures 
that can be used in the game this is based on our own interpretation of a open-ended 
evolutionary algorithm in which the evolution of the elements is not guided towards 
a single objective but rather is free to evolve and generate novelty or diversity 
in this case diversity of structures which the system can later select composites 
from in order to decide what will confomr a level, this data is saved in groups that represent a population 
that can evolve by an evolutionary algorithm in order to create more complex levels.
 This elements of a population are then evaluated by how complex they become and how 
 different they are from the rest of the group in order to create a variety of possible 
 levels to be played.

@@

% What is learned?
After concluding this paper we expect to identify the places were a evolutionary 
algorithm can be used alongside procedural content generation applied to video games
in order to be able to clarify in which areas a evolutionary algorithm can used 
to further improve video game development cycles.

>>>>

\begin{abstract}
% We do not say this project, is more like: In this paoer an evolutionary ... 
% is presented or In this paper we present a .... (in third or first person plural) - MG   
In this paper an evolutionary computation-based system is proposed to generate 
levels for the Angry Birds video game, the levels themselves are composed of a 
set of birds that the player can use, a certain amount of pigs that must be destroyed 
in order to progress to the next level and a given number of pieces that conform 
structures that may or may not protect the pigs from the player. The focus in this stage
is the generation of diverse structures that can be played in the game having the
additional characteristics of being interesting and playable. We propose a 
multi-layered search, first contructing composite structures from basic components, to then
build more complex structures building from these components, following an open-ended 
evolution approach; in which the evolution of structures is not guided towards 
a single objective but rather is free to evolve and generate novelty or diversity. 
The objective is then that the proposed levels are evaluated by how complex they become and how 
different they are from the rest of the group.
%The experiments conducted show  
% We found that in the experiments conducted, levels generated where ...

@@

% What is learned?
%We identify the places were an evolutionary algorithm can be used alongside
%procedural content generation applied to video games in order to be able to
%clarify in which areas an evolutionary algorithm can used to further improve
%video game development cycles.

% En este trabajo se generan estructuras con mayor diversidad y por lo tanto 
% resultan ser interesantes.
